\documentclass[margin, 10pt]{res}% Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{color}
\setlength{\textwidth}{5.3in} % Text width of the document
\setlength{\textheight}{10in}
\begin{document}

%----------------------------------------------------------------------------------------
%   NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
\moveleft.5\hoffset\centerline{\huge \textbf{Zhaoze Zhou}} % Your name at the top
\addtolength{\topmargin}{-.5in}
\moveleft\hoffset\vbox{\hrule width \resumewidth height 2pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{360 Huntington Ave., Boston, MA-02115} % Your address
%\moveleft.5\hoffset\centerline{zhaozezh@ccs.neu.edu}
\moveleft.5\hoffset\centerline{\textcolor{blue}{E-mail: zhaozezh@ccs.neu.edu}
\,\,\,\,\,\,\,\,\,
Tel: (617)-893-3554}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%   OBJECTIVE SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\definecolor{mygrey}{gray}{.85}
%\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\section{EDUCATION}

{\sl MS in Computer Science,}
 Northeastern University \hfill Sept. 2013 - Dec. 2015 \\
 Related Courses: Introduction to Database Management, Algorithm,Computer System,  Fundamentals of Computer Networking, Information Retrieval.\\[0.1in]
{\sl BS in Computer Science,}
 SC University for Nationalities\hfill Sep 2009 - Jun 2013 \\
 Related Courses: Computer Network, JavaEE, Design and Analysis of Algorithm, Operating System, Data Structure


%----------------------------------------------------------------------------------------
%   Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS}

{\sl Operating system:} Unix/Linux, Mac OS X, MS Windows \\
{\sl Languages:} C/C++, Java, Python, DrRacket, Swift \\
{\sl Java Technologies:} Servlets, JDBC, JPA \\
{\sl Web Technologies:} JSP, ASP.NET, XML, HTML, JavaScript, CSS, DOM, REST\\
{\sl Databases:} Microsoft SQL Server, MySQL, MS Access\\
{\sl Tool:} Git, ElasticSearch, Maven, Vim, Emacs, UML\\
%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Professional \\ EXPERIENCE}
{\sl Software Engineer Intern} \hfill  Jun 2014 - Dec 2014 \\
 Samsung Research America, Cambridge, MA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Improved the reliability of the Gyp build system.
\item Ported chromium C++ code to Tizen browser and wrote test cases.
\item Maintained internal trunk with C++, Python, HTML, CSS and JavaScript.
\item Open-Source working experience.
\end{itemize}

%----------------------------------------------------------------------------------------
%   Project SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Project \\ EXPERIENCE}

{\sl Python Search Engine Project} \hfill Jan. 2015 - Present
\begin{itemize}
\item Developed a web crawler to crawl and extract very large amount of documents from Internet.
\item Implemented PageRank algorithm to rank the websites crawled by web crawler and implemented information evaluation function to evaluate the result.
\item Implemented several indexes for large number of documents with limit memory usage.
\item Implemented different retrieval models based on ElasticSearch Index.
\end{itemize}

{\sl Computer Network Project }\hfill Jan. 2015 - Present
\begin{itemize}
\item Implemented IP and TCP header for raw socket, and download files using raw socket.
\item Analyzed the performance of TCP variants under various of conditions in NS-2 platform.
\end{itemize}
{\sl Developed a Real Estate System: An Android application based on OData Protocol with MySQL Database} \hfill Sept.2013 - Dec.2014
\begin{itemize}
\item Designed use-cases, relational model for the Real Estate Database
\item Developed Android client that provide multiple operations using OData protocol to the Database
\end{itemize}


{\sl Developed an On-line Chatting System: using JavaEE with SQLite Database to provide basic needs for online chatting system} \hfill Dec. 2011\\


%----------------------------------------------------------------------------------------
%   EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
